### 2025-06-18 thesis_julio/Chapter3/chapter3.tex
18june
18jun2

For obtaining the important parameters on the vdm scan we return to the equation (1.2) and apply it to and individual bunch crossing, the values of N1 and N2 being the number of protons colliding can be obtained since is a known quantity from the experiment, the frequency f is also a known quantity, the frequency of the LHC which is 11,245 kHz but the proton densities $\rho_{1}$ and $\rho{2}$ are more difficult to obtain, this is were the vdM scan help us to measure integral over the bunch proton densities. The luminosity integral evaluated with the beams separated by a distance $\Delta_{x}$ and $\Delta_{y}$ can take the form of:

@@

Similarly to the previous step we can obtain the value of the other factor of (3.2) with an analogous process. The integrals resulting on the right side can be evaluated by evaluated by obtaining the rate in function of the beam-beam separation which are $\Delta x$ and $\Delta y$  this because the luminosity has a linear relationship with the rate. The Luminosity can be expresed on terms of the rate during the head on positions, R(\Delta_{x0}, \Delta_{y0}) like in the equation (3.5)

\begin{equation}
L(\Delta x, \Delta y) = N_{1} N_{2} f \frac{2R(\Delta x_{0}, \Delta y_{0}){\int L(\Delta x_{0}, \Delta y) d(\Delta y) \int L(\Delta x, \Delta y_{0}) d(\Delta x)}}
\end{equation}

@@

\begin{equation}
\sigma_{visible} = 1460890 \pm 546
\end{equation}

@@

Starting for the Background there were analysis made with the QG model fit which doesn't extract the background PCC, the sigma visible obtained in this case was of $\sigma_{visnobg}$ = 1452589 compared to the value that we obtained $\sigma_{vis}$ = 1450890 can be concluded that the uncertainty is 0.11\%.

@@

\begin{table} [H]
\begin{center}
\caption{Bunch to bunch uncertainty table.}
\begin{tabular}{|c c c c|} 
 \hline
 Scan & \sigma_{vis} & STD & Syst. Error  \\ [0.5ex] 
 \hline\hline
 vdM1 & 1463330 & 1220 & 0.02  \\ 
 \hline
 vdM2 & 1453795 & 1212 & 0.02 \\
 \hline
 vdM3 & 1464237 & 953 & 0.01 \\
 \hline
 vdM4 & 1454363 & 1170 & 0.02 \\
 \hline
 vdM5 & 1465271 & 1200 & 0.02  \\ 
 \hline
 BI1 & 1457208 & 1169 & 0.02 \\ 
 \hline
 BI2 & 1464367 & 1233 & 0.02\\
 \hline
 vdM6 &1462515  & 1155 & 0.02 \\ 
 \hline
    \textbf{mean}        &             &            & 0.2 \\ [1.0ex]
 \hline
\end{tabular}
\end{center}
\end{table}

>>>>

For obtaining the important parameters on the vdm scan we return to the equation (1.2) and apply it to and individual bunch crossing, the values of N1 and N2 being the number of protons colliding can be obtained since is a known quantity from the experiment, the frequency f is also a known quantity, the frequency of the LHC which is 11,245 kHz but the proton densities $\rho_{1}$ and $\rho{2}$ are more difficult to obtain, this is were the vdM scan help us to measure integral over the bunch proton densities. The luminosity integral evaluated with the beams separated by a distance $\Delta_{x}$ and $\Delta_{y}$ can take the form of shown ins equation (3.1)

@@

Similarly to the previous step we can obtain the value of the other factor of (3.2) with an analogous process. The integrals resulting on the right side can be evaluated by evaluated by obtaining the rate in function of the beam-beam separation which are $\Delta x$ and $\Delta y$  this because the luminosity has a linear relationship with the rate. The Luminosity can be expresed on terms of the rate during the head on positions, $R(\Delta_{x0}, \Delta_{y0})$ like in the equation (3.5)

\begin{equation}
L(\Delta x, \Delta y) = N_{1} N_{2} f \frac{2R(\Delta x_{0}, \Delta y_{0})}{\int L(\Delta x_{0}, \Delta y) d(\Delta y) \int L(\Delta x, \Delta y_{0}) d(\Delta x)}
\end{equation}

@@

\begin{equation}
\sigma_{visible} = 1460890 \mu b \pm 546
\end{equation}

@@

Starting for the Background there were analysis made with the QG model fit which doesn't extract the background PCC, the sigma visible obtained in this case was of $\sigma_{visnobg}$ = 1452589 $\mu b$ compared to the value that we obtained $\sigma_{vis}$ = 1450890 $\mu b$ can be concluded that the uncertainty is 0.11\%.

@@

\begin{table} [H]
\begin{center}
\caption{Bunch to bunch uncertainty table.}
\begin{tabular}{|c c c c|} 
 \hline
 Scan & \sigma_{vis} \mu b & STD & Syst. Error  \\ [0.5ex] 
 \hline\hline
 vdM1 & 1463330 & 1220 & 0.02  \\ 
 \hline
 vdM2 & 1453795 & 1212 & 0.02 \\
 \hline
 vdM3 & 1464237 & 953 & 0.01 \\
 \hline
 vdM4 & 1454363 & 1170 & 0.02 \\
 \hline
 vdM5 & 1465271 & 1200 & 0.02  \\ 
 \hline
 BI1 & 1457208 & 1169 & 0.02 \\ 
 \hline
 BI2 & 1464367 & 1233 & 0.02\\
 \hline
 vdM6 &1462515  & 1155 & 0.02 \\ 
 \hline
    \textbf{mean}        &             &            & 0.2 \\ [1.0ex]
 \hline
\end{tabular}
\end{center}
\end{table}

### 2025-06-18 thesis_julio/Chapter4/chapter4.tex
18jun2

The obtained value for the calibration constant was $\sigma_{visible}$ = 1460890 \pm 546$ the analysis and results reported in this work will be useful for an analysis of the pre eliminary luminosity measurement for Run 3 in the CMS experiment of the lHC, where the rest of the luminometers and It's certainties will be studied along with this one.

>>>>

The obtained value for the calibration constant was $\sigma_{visible}$ = 1460890 $\mu b$ \pm 546 \pm 6281(systematics)$ the analysis and results reported in this work will be useful for an analysis of the pre eliminary luminosity measurement for Run 3 in the CMS experiment of the lHC, where the rest of the luminometers and It's certainties will be studied along with this one.
